Quantifying and controlling biases in dark matter halo concentration estimates

### 2016-08-25 paper/ms.tex
KS test. Mencionado en el paper y en el reply

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJL}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}
\usepackage{graphics}
\usepackage[dvips]{epsfig}

@@

In our bootstrapping experiments we take halos sampled with at least
$10^{5}$ particles and subsample each halo by factors of $2$ up to
$10^{3}$ to measure the concentration every time the halo is
resampled. 
Every time we keep fixed the virial radius and the center found for
the high resolution halo.
We tested that leaving the virial radius and center free in each
bootstrapping iteration has an effect smaller than $1\%$ in the
concentration. 
We extract in total 10000 bootstrapping samples for the Bolshoi
and the Via Lactea simulations.
In the Bolshoi simulation we select 14 massive halos and create 700
subsamples for each one.  
For the Via Lactea simulation the same halo is subsampled 10000
times.

@@

 The authors acknowledge the technical support from the new
 high-performance computing facility at Uniandes. JEFR acknowledges
 financial support from Vicerrector\'ia de Investigaciones at Uniandes
 through a FAPA project. JCMC acknowledges financial support from
 ``Estrategia de  sostenibilidad 2014-2015, Universidad de
 Antioquia''.

>>>>

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJL}}
\usepackage{multirow,color,wrapfig}
\usepackage {graphicx}
\usepackage{graphics}
\usepackage[dvips]{epsfig}

@@

In our bootstrapping experiments we take halos sampled with at least
$10^{5}$ particles and subsample each halo by factors of $2$ up to
$10^{3}$ to measure the concentration every time the halo is
resampled. 
We use a two-sample Kolmogorov-Smirnov (KS) test to check that the
bootstrapped sets are a fair subsample of the parent halo.
Using the KS test we compare the list of radial distances from each
subsample against that of its parent halo.
We find that the resulting p-value distribution is flat.
This confirms that the radial distribution of particles in the
bootraped halo is consistent with coming from the distribution given
by the parent halo.

For every subsample we keep fixed the virial radius and the center
found for the high resolution halo.
Leaving the virial radius and center free in each bootstrapping
iteration has an effect smaller than $1\%$ in the concentration. 
We extract in total 10000 bootstrapping samples for the Bolshoi
and the Via Lactea simulations.
In the Bolshoi simulation we select 14 massive halos and create 700
subsamples for each one.  
For the Via Lactea simulation the same halo is subsampled 10000
times.

@@

 The authors acknowledge the technical support from the new
 high-performance computing facility at Uniandes. JEFR acknowledges
 financial support from Vicerrector\'ia de Investigaciones at Uniandes
 through a FAPA project. JCMC acknowledges financial support from
 ``Estrategia de  sostenibilidad 2014-2015, Universidad de
 Antioquia''. The authors also thank Tom\'as Verdugo, Stefan
 Gottloeber and Nelson Padilla for their comments on earlier version
 of this work.
